---
title: "Shah Nawaz <br> Curriculum vitae"
output:
  pagedown::html_paged:
    css: ["css/bootstrap-5.2.1.min.css", "css/two-col-cv.css"]
    number_sections: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
library(lubridate)
source("R/utility-functions.R")

cv_entries <- read_excel("cv_data.xlsx", sheet = "cv_entries") |> 
  mutate(year = year(date))
publications <- read_excel("cv_data.xlsx", sheet = "publications") |> 
  mutate(year = year(date))
```


::: {.row}

:::::: {.col-8 .summary}

# Professional summary
**Aims**---to develop efficient techniques for analysis of data that help organizations for future decison making.\
**Methods**---ggplot, matplotlib, powerBI, web scraping, machine learning, report writing.
::::::

:::::: {.col-4}

# Contact {.box}

::::::::: {.info-box}

| Center | Left |
|:------:|:-----|
| `r fa("map-marker-alt")`| 3SR research labotory, University of Grenoble Alpes |
| `r fa("envelope")` | shah.nawaz@univ-grenoble-alpes.fr |
| `r fa("globe")` | [LinkedIn](https://linkedin.com/in/shah-nawaz) |
| `r fa("github")` | [Github](https://github.com/shahnawaz323) |
 
:::::::::

::::::

:::

::: {.row}



:::::: {.col-6 .right}

# Education

```{r}
cv_entries |> 
  filter(type == 'education') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |> 
  select(year, what) |> 
  kable()
```

# Selected teaching experience
```{r}
cv_entries |> 
  filter(type == 'teaching', short_cv == "y") |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
         "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```

# Technical skills
```{r}
cv_entries |> 
  filter(type == 'technical') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}")) |> 
  select(what, additional_info) |> 
  kable()
```
::::::

:::::: {.col-6 .left}

# Data analysis and visualization
```{r}
cv_entries |> 
  filter(type == 'work', exclude == "n") |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {additional_info}<br>")) |> 
  select(what) |> 
  kable()


```

# Volunteering
```{r}
cv_entries |>
  filter(type == 'volunteering') |>
  filter(exclude == "n") |>
  mutate(what = glue("<span class='cv-entry-title'>{what}")) |>

  arrange(desc(date), desc(date_end)) |> 
  select(what, additional_info) |>
  kable()
```

# Languages
```{r}
cv_entries |> 
  filter(type == 'languages') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}")) |> 
  select(institution, what, additional_info) |> 
  kable()
```

keywords
```{r}
cv_entries |> 
  filter(type == 'keywords') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>")) |> 
  select(what) |> 
  kable()
```
::::::
:::
